Race Science in Mainstream Psychology, 1960-2010

### 2024-04-15 paper/paper.qmd
first pass integrating proof-of-concept

format: 
  elsevier-pdf:
    journal: 
      name: "journal"
    keep_tex: true
    latex_engine: "xelatex"
    number-sections: false
    link-citations: true

@@

# header-includes:
#  - \usepackage{lineno}
#  - \linenumbers
---

<!-- NHB submission guidelines: <https://www.nature.com/nathumbehav/submission-guidelines> -->

@@

>>>>

format: 
  elsevier-pdf:
    journal: 
      name: "journal"
    keep_tex: true
    latex_engine: "xelatex"
    number-sections: false
    link-citations: true
    mathspec: true

@@

# header-includes:
#  - \usepackage{lineno}
#  - \linenumbers

execute:
  cache: true
---

@@

### Proof of concept

{{< include ../scripts/11-proof-of-concept.qmd >}}
